% UniKL Thesis style, prepared by Dr. Mohammad Nauman (nauman@csrdu.org) and Dr. Sohail (sohail@unikl.edu.my), modified by Dr Norhaidah for FYP Bachelor of Software Engineering.

% Change your information accordingly. 

\authorName{Wan Aminnur Rasheed Wan Zainol} %Write your name here
\authorEmail{aminnur.zainol@s.unikl.edu.my} % Write your email
\authorID{0142595464} % UniKL id
\authorSemester{Semester 6} % Semester
\degreeName{Bachelor of Information Technology (Hons) in Software Engineering } % Write your Bachelor course
\date{June 30, 2025}

\thesisTitle{COLLECTIVE - A NOTE-TAKING / JOURNALING APPS WITH AI ANALYTICS} % Write your title here
\supervisorName{Mdm. Suzana Bt. Kasim} % Write your Supervisor name
\accessorName{Dr. Mohd Faizuddin Md Noor} % Write your Accessor Name

\deptName{Malaysian Institute of Information Technology} % Write your campus name
\universityName{Universiti Kuala Lumpur}

\titlePageNotice{
Report Submitted to Fulfill the Partial Requirements \\
For the \VdegreeName\  \\ 
%\VdeptName\ \\
\VuniversityName\ \\
}
% Write  your acknowledgement here
\acknowledgementText{

I would like to express my sincere gratitude to my supervisor, Mdm. Suzana Bt. Kasim, for her invaluable guidance, patience, and continuous support throughout this research project. Her expertise and insights have been instrumental in shaping this work.

I am equally grateful to my assessor, Dr. Mohd Faizuddin Md Noor, for his valuable feedback and constructive criticism that helped improve the quality of this thesis.

My appreciation extends to the Malaysian Institute of Information Technology, Universiti Kuala Lumpur, for providing the necessary resources and facilities that made this research possible.

I would also like to thank my family and friends for their unwavering support and encouragement throughout my academic journey. Their understanding and motivation have been a source of strength during challenging times.

Finally, I acknowledge all the participants who volunteered for the usability testing and provided valuable feedback that contributed to the development and improvement of the Collective mobile journaling application.

} 





